Shaping the Perception of a Robot by Cognitive Priming

### 2016-09-05 main.tex
Refine hypotheses

Our methodology involves showing participants video stimuli that elicit
different levels of anthropomorphism, and measuring gaze fixations over the
course of the video clips. To be suitable for an eye-tracking experiment, the
video stimuli must be visually identical between conditions, and we therefore
rely on non-visual cues to elicit different anthropomorphic projections
(cognitive priming). The next section details this methodology.

This approach allows us to decompose the hypothesis \h{} into two simpler
hypotheses \h{1} and \h{2}:  we want first to verify that cognitive priming
enables us to effectively create stimuli that induce lower or higher attribution
of human-likeness to robots (\h{1}).  We need next to verify that in the case of
high anthropomorphic attributions, the participants' gaze will be directed
significantly more towards the head of the robot than in the case of low
anthropomorphic attributions (\h{2}).

If verified, these hypotheses would allow us to conclude that in a given
human-robot interaction situation, the more a human focuses on the robot's head,
the more the human ascribe anthropomorphic features to the robot.
\fixme{Attention, this conclusion seems to wrongly reverse the implication of
the hypotheses!}

%If verified, it
%effectively means that the expectations held by the participants regarding the
%cognitive capabilities of the robot are reflected by the eye fixations on the
%head of the robot.  The hypothesis can be tested by comparing gaze fixations in
%the two conditions (\emph{human-like} \vs \emph{machine-like}).

@@

\begin{itemize}
    \item people who tend to anthropomorphise a lot show gazing behaviours that
        are similar for humans and robots, while people who show a lower
        tendency to anthropomorphise do not look at robots and humans in the
        same way (\h{3}). If this is verified, this would confirm that our
        gazing behaviour towards agents is impacted by our tendency to
        anthropomorphise.

@@

\section{Conclusion}

>>>>

Our methodology involves showing participants video stimuli that elicit
different levels of anthropomorphism, and measuring gaze fixations over the
course of the video clips. To be suitable for an eye-tracking experiment, the
video stimuli must be visually identical between conditions, and therefore
we have to rely on non-visual cues to elicit different anthropomorphic
projections. We choose to use cognitive priming with audio cues, as detailed in
the next section.

This approach allows us to decompose the hypothesis \h{} into two simpler
hypotheses \h{1} and \h{2}: we want first to verify that cognitive priming
enables us to effectively manipulate the attribution of human-likeness to robots
(\h{1}).  We need next to verify that in the case of higher anthropomorphic
attributions, the participants' gaze will be directed significantly more towards
the head of the robot than in the case of low anthropomorphic attributions
(\h{2}).

If verified, these hypotheses would allow us to conclude that in a given
human-robot interaction situation, gaze fixations on a robot's head reflects the
ascription of anthropomorphic features to the robot. This would suggest that a
relatively simple biometric and in-the-moment measure (eye-tracking) can
effectively inform us about occurring anthropomorphic projections.

@@

\begin{itemize}
    \item people who generally tend to anthropomorphise exhibit gazing
        behaviours that are similar when looking either at humans or robots, and
        reciprocally (\h{3}). If this is verified, this would confirm that our
        gazing behaviour towards agents is impacted by our tendency to
        anthropomorphise.

@@

\section{Conclusion}
\labe{conclusion}
